Secure Composition of Robust and Optimising Compilers

### 2023-06-13 popl/main.tex
TMS monitor definition
title, summary

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[acmsmall,review,screen,dvipsnames]{acmart}

\usepackage[colorinlistoftodos]{todonotes}
\usepackage[inference]{semantic}
\usepackage{fontawesome5}
\usepackage{glossaries}
\usepackage{cleveref}
\usepackage{stmaryrd}
\usepackage{listings}
\usepackage{xspace}

@@

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Composing Robustly Safe Compilers}

@@

\begin{center}\small\it
	{In the following, we use syntax highlighting accessible to both colourblind and black \& white readers~\citep{patrignani2020use}. Specifically, we use a $\src{\text{blue}}$,
	$\src{sans\text{-}serif}$ font for $\src{L_{TMS}}$,
	$\trg{bold}$ font for $\trg{L}$ and $\trg{L_{MS}}$, and $\obj{green}$ font for $\obj{L_{sCCT}}$.
	}
\end{center}
\end{abstract}

@@

\BrText{Solution}{This paper introduces a formal framework for secure compiler compositions and showcases the framework's power by instantiating it on a multi-level compilation chain.
To this end, we discuss security property compositions and define several secure compilers, where each is either robustly preserving a different security property of interest or optimizing, i.e., applying \gls{cf} or doing \gls{dce}.
We compose these secure compilers into a multi-level compilation chain which is optimizing and robustly preserves a combination of \gls{ms} and \gls{cct}.
Crucially, the robust preservation proofs are only done for the individual compilers in the compilation chain and the robust preservation for the whole chain is a result of one of our key theorems.
The key results are formalized in Coq.}

@@

Security tags describe wether an event contains sensitive information ($\lock$) or not ($\unlock$).
Control tags state wether the context ($\ctx$) or the component ($\comp$) are responsible for emitting the event.
Pre-events describe the actual kind of event that happened.
$\ev{Alloc\ \loc\ n}$ states that an allocation of size $n$ happened and is stored at $\loc$.
$\ev{Dealloc\ \loc}$ announces that location $\loc$ is freed.
$\ev{Use\ \loc\ n}$ abstracts over reads from $\loc$ and writes to $\loc$ in memory, where $n$ is read/written, respectively.
$\ev{Branch\ n}$ and $\ev{Binop\ n}$ leak values involved in a branch or in a binary operation with data-dependent execution time.
Finally, events are either the emptyevent ($\emptyevent$), a program crash ($\lightning$), or a tuple consisting of a pre-event, a control tag, and a security tag.

@@

\paragraph{\glsfirst{tms}}
\paragraph{\glsfirst{sms}}
\paragraph{\glsfirst{ms}}
\paragraph{\glsfirst{scct}}

>>>>

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% The first command in your LaTeX source must be the \documentclass command.

% Fixing: Too many math alphabets used in version normal.
\newcommand\hmmax{0}
\newcommand\bmmax{0}
\documentclass[acmsmall,review,screen,dvipsnames]{acmart}

\usepackage[colorinlistoftodos]{todonotes}
\usepackage[inference]{semantic}
\usepackage{fontawesome5}
\usepackage{glossaries}
\usepackage{cleveref}
\usepackage{stmaryrd}
\usepackage{listings}
\usepackage{xspace}
\usepackage{bm}

@@

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Secure Composition of Robust and Optimising Compilers}

@@

\begin{center}\small\it
	{In the following, we use syntax highlighting accessible to both colourblind and black \& white readers~\citep{patrignani2020use}. 
	Specifically, we use a $\src{blue}$, $\src{sans\text{-}serif}$ font for our $\src{source}$,
	a $\trg{red}$, $\trg{bold}$ font for our $\trg{intermediate}$, 
	and a $\obj{green}$, $\obj{teletype}$ font for $\obj{target}$ language.
	}
\end{center}
\end{abstract}

@@

\BrText{Solution}{
This paper introduces a formal framework for secure compiler compositions and showcases the framework's power by instantiating it on a multi-level compilation chain.
To this end, we discuss security property compositions and define several secure compilers, where each is either robustly preserving a different security property of interest or optimizing, i.e., applying \gls{cf} or doing \gls{dce}.
We compose these secure compilers into a multi-level compilation chain which is optimizing and robustly preserves a combination of \gls{ms} and \gls{cct}.
Crucially, the robust preservation proofs are only done for the individual compilers in the compilation chain and the robust preservation for the whole chain is a result of one of our key theorems.
The key results are formalized in Coq.}

% keyword: pass
\MPin{
	commands missing
}
This paper introduces a framework for reasoning about the composition of secure and optimising compiler passes and it showcases the power of this framework by instantiating it on a multi-pass compilation chain.
To this end, this paper first discusses how to compose security properties, such as temporal and spatial memory safety into general memory safety, and cryptographic constant time.
Then, this paper defines several secure compiler passes, where each is either preserving a different security property (e.g., temporal or spatial memory safety) or performing a security-preserving optimisation, (e.g., applying constant-folding or dead-code elimination).
% keyword- end to end, composition
Finally, this paper shows how to compose these secure compiler passes into a multi-pass compilation chain which can be proven to provide end-to-end preservation of general memory safety and cryptographic constant time. 
Crucially, this end-to-end security preservation is obtained by having each compilation pass (i) preserve a sub-part of the overall security property individually and then (ii) compose each preserved security property as dictated by our framework.
Our results showcase how our framework allows the kind of formal security reasoning that compiler writers already want (and do), obtaining precise, compositional security reasoning while providing minimal (and modular) proof effort.
\MPin{
	last line: not the best.
}

@@

Security tags describe wether an event contains sensitive information ($\lock$) or not ($\unlock$).
Control tags state wether the context ($\ctx$) or the component ($\comp$) are responsible for emitting the event.
Pre-events describe the actual kind of event that happened.
$\ev{Alloc\ \loc\ n}$ states that an allocation of size $n$ happened and is stored at $\loc$.
Locations $\loc$ are elements of $L$ and left abstract.
However, we expect $L$ to be closed over addition with natural numbers.
$\ev{Dealloc\ \loc}$ announces that location $\loc$ is freed.
$\ev{Use\ \loc\ n}$ abstracts over reads from $\loc$ and writes to $\loc$ in memory, where $n$ is read/written, respectively.
$\ev{Branch\ n}$ and $\ev{Binop\ n}$ leak values involved in a branch or in a binary operation with data-dependent execution time.
Finally, events are either the emptyevent ($\emptyevent$), a program crash ($\lightning$), or a tuple consisting of a pre-event, a control tag, and a security tag.

@@

\paragraph{Monitor for \glsfirst{tms}}
\begin{gather*}
  \begin{aligned}
    \mi{(Abstract\ Store)}~\tmsmonitor\bnfdef&\ \left\{\text{alloced}:L,\text{freed}:L\right\}\\
    \mi{(Abstract\ Events)}~\absevent\bnfdef&\ \absev{\emptyevent} \mid \absev{Alloc\ }\loc \mid \absev{Dealloc\ }\loc \mid \absev{Use\ }\loc \mid \absterm\\[0.33cm]
    \tmsmonitor\subseteq\tmsmonitor[']:=\ &\tmsmonitor.\text{freed}\subseteq\tmsmonitor['].\text{freed} \\
    \loc\in\tmsmonitor:=\ &\loc\in\tmsmonitor.\text{alloced}\text{ and }\loc\notin\tmsmonitor.\text{freed} \\
    \loc\notin\tmsmonitor:=\ &\loc\notin\tmsmonitor.\text{alloced}\text{ and }\loc\notin\tmsmonitor.\text{freed} \\
    \left\{\loc\right\}\cup\tmsmonitor:=\ & \left\{\text{alloced}:\left\{\loc\right\}\cup\tmsmonitor.\text{alloced},\text{freed}:\tmsmonitor.\text{freed}\right\}\\
    \tmsmonitor\setminus\left\{\loc\right\}:=\ &\left\{\text{alloced}:\tmsmonitor.\text{alloced}\setminus\left\{\loc\right\}, \text{freed}:\tmsmonitor.\text{freed}\cup\left\{\loc\right\}\right\}\\
  \end{aligned}
\end{gather*}

\paragraph{Monitor for \glsfirst{sms}}
\begin{gather*}
  \begin{aligned}
  \end{aligned}
\end{gather*}
\paragraph{Comining Monitors: \glsfirst{ms}}

\paragraph{Monitor for \glsfirst{scct}}
\begin{gather*}
  \begin{aligned}
  \end{aligned}
\end{gather*}
